The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2018-05-19 Paper.Rmd
adding results and description for anolis data

#### Non-parametric analysis of tail dependence \label{Ex_contrasts_67_NPA}
<!--we have to add description here after DAN fixes bug(?) in bivfunctionplot.R-->

>>>>

#### Non-parametric analysis of tail dependence \label{Ex_contrasts_67_NPA}

As described in \nameref{Methods}, each of our statistics, are computed for $(l_b,u_b)$ in the 
ranges $0-0.25$, $0.25-0.5$, $0.5-0.75$, $0.75-1$ (with $4$ number of bins). Anolis data set has lesser number of data compared to other two bivariate data set, so fewer number of bins were chosen to measure tail-dependence.
Those statistics were compared to the distributions of values of the same statistic with the same ranges computed on 1000 normal-copula surrogate datasets with similar Kendall or Spearman correlations, in different 
runs for Kendall and Spearman (Fig. \ref{SM-fig_contrasts_67_nonparam}).

Results indicate that tail dependence of 
data is stronger in both the lower and upper tails than would be expected under a 
null hypothesis of a normal copula, answering the second part of question 1.

We also tested statistically for asymmetry of tail dependence, which seems visible in Fig. \ref{SM-fig_raw_cop_AVG_humerus_ltoe}(B). Results (Table \ref{SM-tab_contrasts_67_asym}) show that upper-tail dependence was, indeed, significantly stronger than lower-tail dependence in these data, answering the third part of question 1.
